---
title: "Team Dynamics"
output: html_notebook
---

###Loading Packages; These Packages Must Be Installed Prior to Loading###
```{r}
suppressPackageStartupMessages(library(psych))
suppressPackageStartupMessages(library(readxl))
suppressPackageStartupMessages(library(moments))
suppressPackageStartupMessages(library(lavaan))
suppressPackageStartupMessages(library(sem))
suppressPackageStartupMessages(library(semPlot))
suppressPackageStartupMessages(library(gplots))
```
###Load Data Sets; The Arguement for this Function Varies Depending on Local File Source###
```{r}
TeamDynamicsData <- read_excel("C:/Users/Domiv_000/Desktop/School/Thesis/Data/TeamDynamicsData.xlsx")
View(TeamDynamicsData)
TeamDynamicsDataFull <- read_excel("C:/Users/Domiv_000/Desktop/School/Thesis/Data/TeamDynamicsDataFull.xlsx")
View(TeamDynamicsDataFull)
```
###Check Construct Reliability###
```{r}
StereotypeThreatConstruct <- data.frame(TeamDynamicsDataFull$`StereotypeThreat-1`, 
                                        TeamDynamicsDataFull$`StereotypeThreat-2`,
                                        TeamDynamicsDataFull$`StereotypeThreat-3`)
alpha(x = StereotypeThreatConstruct, title = "Stereotype Threat Reliability")

CommunalGoalAffordanceConstruct <-
      data.frame(TeamDynamicsDataFull$`CommunalGoalFulfillment-TaskFull`,
                 TeamDynamicsDataFull$`CommunalGoalFulfillment-CareerFull `,
                 TeamDynamicsDataFull$`CommunalGoalFulfillmentShort-WorkingWithPeople`,
                 TeamDynamicsDataFull$`CommunalGoalFulfillmentShort-HelpingOthers`,
                 TeamDynamicsDataFull$`CommunalGoalFulfillmentShort-ServingCommunity`)
alpha(x = CommunalGoalAffordanceConstruct, title = "Communal Goal Affordance Reliability")

AgenticGoalAffordanceConstruct <- 
      data.frame(TeamDynamicsDataFull$`AgenticGoalFulfillment-TaskFull`,
                 TeamDynamicsDataFull$`AgenticGoalFulfillment-CareerFull`,
                 TeamDynamicsDataFull$`AgenticGoalFulfillmentShort-Achievement`,
                 TeamDynamicsDataFull$`AgenticGoalFulfillmentShort-Power`,
                 TeamDynamicsDataFull$`AgenticGoalFulfillmentShort-Experiences`,
                 TeamDynamicsDataFull$`AgenticGoalFulfillmentShort-Excitement`)
alpha(x = AgenticGoalAffordanceConstruct, title = "Agentic Goal Affordance Reliability")

StateAnxietyConstruct <- data.frame(TeamDynamicsDataFull$`StateAnxiety-1`,
                                    TeamDynamicsDataFull$`StateAnxiety-2RC`,
                                    TeamDynamicsDataFull$`StateAnxiety-3`,
                                    TeamDynamicsDataFull$`StateAnxiety-4`,
                                    TeamDynamicsDataFull$`StateAnxiety-5RC`,
                                    TeamDynamicsDataFull$`StateAnxiety-6RC`,
                                    TeamDynamicsDataFull$`StateAnxiety-7RC`,
                                    TeamDynamicsDataFull$`StateAnxiety-8`,
                                    TeamDynamicsDataFull$`StateAnxiety-9RC`,
                                    TeamDynamicsDataFull$`StateAnxiety-10`,
                                    TeamDynamicsDataFull$`StateAnxiety-11`,
                                    TeamDynamicsDataFull$`StateAnxiety-12`)
alpha(x = StateAnxietyConstruct, title = "State Anxiety Reliability")

BelongingConstruct <- data.frame(TeamDynamicsDataFull$`Belonging-1`,
                                 TeamDynamicsDataFull$`Belonging-2`,
                                 TeamDynamicsDataFull$`Belonging-3`)
alpha(x = BelongingConstruct, title = "Belonging Reliability")

ScienceMotivationConstruct <- data.frame(TeamDynamicsDataFull$`ScienceMotivation-1`,
                                         TeamDynamicsDataFull$`ScienceMotivation-2`,
                                         TeamDynamicsDataFull$`ScienceMotivation-3`,
                                         TeamDynamicsDataFull$`ScienceMotivation-4RC`,
                                         TeamDynamicsDataFull$`ScienceMotivation-5`,
                                         TeamDynamicsDataFull$`ScienceMotivation-6`,
                                         TeamDynamicsDataFull$`ScienceMotivation-7`,
                                         TeamDynamicsDataFull$`ScienceMotivation-8`,
                                         TeamDynamicsDataFull$`ScienceMotivation-9`,
                                         TeamDynamicsDataFull$`ScienceMotivation-10`)
alpha(x = ScienceMotivationConstruct, title = "Science Motivation Reliability")

ScienceDomainIdentificationConstruct <- data.frame(
      TeamDynamicsDataFull$`ScienceDomainIdentification-1`,
      TeamDynamicsDataFull$`ScienceDomainIdentification-2`,
      TeamDynamicsDataFull$`ScienceDomainIdentification-3`,
      TeamDynamicsDataFull$`ScienceDomainIdentification-4`,
      TeamDynamicsDataFull$`ScienceDomainIdentification-5`,
      TeamDynamicsDataFull$`ScienceDomainIdentification-6`)
alpha(x = ScienceDomainIdentificationConstruct, 
      title = "Science Domain Identification Reliability")

PartnerRatingsConstruct <- data.frame(TeamDynamicsDataFull$`PartnerRatings-Friendliness`,
                                      TeamDynamicsDataFull$`PartnerRatings-Competency`,
                                      TeamDynamicsDataFull$`PartnerRatings-Condescention`,
                                      TeamDynamicsDataFull$`PartnerRatings-Appropriatness `,
                                      TeamDynamicsDataFull$`PartnerRatings-Welcomingness`,
                                      TeamDynamicsDataFull$`PartnerRatings-Respectfulness`,
                                      TeamDynamicsDataFull$`PartnerRatings-Talk`,
                                      TeamDynamicsDataFull$`PartnerRatings-HangOut`,
                                      TeamDynamicsDataFull$`PartnerRatings-WorkWith`,
                                      TeamDynamicsDataFull$`PartnerRatings-Experience`)
alpha(x = PartnerRatingsConstruct, title = "Partner Ratings Reliability")

```
###Descriptive Statistics; Descriptives by Condition###
```{r}
attach(TeamDynamicsData)
describe(TeamDynamicsData)
describeBy(x = TeamDynamicsData, group = Condition)
``` 

#Check Assumptions of ANOVA#
```{r}
hist(TeamDynamicsData$StereotypeThreat, main = "", 
     xlab = "Stereotype Threat", 
     xlim = c(1,5), freq = FALSE, col = "Light Blue")
lines(density(TeamDynamicsData$StereotypeThreat))

hist(TeamDynamicsData$CommunalValue, main = "", xlab = "Communal Goal Affordances",
     xlim = c(1, 7), freq = FALSE, col = "Light Blue")
lines(density(TeamDynamicsData$CommunalValue))

hist(TeamDynamicsData$StateAnxiety, main = "", xlab = "State Anxiety", 
     xlim = c(1,5), freq = FALSE, col = "Light Blue")
lines(density(TeamDynamicsData$StateAnxiety))

hist(TeamDynamicsData$Belonging, main = "", xlab = "Belonging", 
     xlim = c(1,7), freq = FALSE, col = "Light Blue")
lines(density(TeamDynamicsData$Belonging))

hist(TeamDynamicsData$FutureMotivation, main = "", xlim = c(1,7),
     xlab = "Future Science Motivation", freq = FALSE,
     col = "Light Blue")
lines(density(TeamDynamicsData$FutureMotivation))

hist(TeamDynamicsData$ScienceMotivation, main = "", xlab = "Science Motivation", 
     xlim = c(1,7), freq = FALSE, col = "Light Blue")
lines(density(TeamDynamicsData$ScienceMotivation))

hist(TeamDynamicsData$ScienceDomainIdentification, main = "", xlim = c(1,5),
     xlab = "Science Domain Identification", freq = FALSE,
     col = "Light Blue")
lines(density(TeamDynamicsData$ScienceDomainIdentification))

hist(TeamDynamicsData$PartnerRatings, main = "", xlab = "Partner Ratings", 
     xlim = c(1,9), freq = FALSE, col = "Light Blue")
lines(density(TeamDynamicsData$PartnerRatings))


```
#Non-Parametric Kruskal-Wallis ANOVAs Due to Violations of Assumptions#
```{r}
#Stereotype Threat X Condition#
kruskal.test(data = TeamDynamicsData, StereotypeThreat~Condition)

#Communal Goal Affordance X Condition#
kruskal.test(data = TeamDynamicsData, CommunalValue~Condition)

#State Anxiety X Condition#
kruskal.test(data = TeamDynamicsData, StateAnxiety~Condition)

#Belonging X Condition#
kruskal.test(data = TeamDynamicsData, Belonging~Condition)

#Future Motivation#
kruskal.test(data = TeamDynamicsData, FutureMotivation~Condition)

#Science Motivation X Condition#
kruskal.test(data = TeamDynamicsData, ScienceMotivation~Condition)

#Science Domain Identification X Condition#
kruskal.test(data = TeamDynamicsData,
             ScienceDomainIdentification~Condition)

#Partner Ratings X Condition#
kruskal.test(data = TeamDynamicsData, PartnerRatings~Condition)
```
#Visualize Group Means by Condition#
```{r}
#Stereotype Threat by Condition#
StereotypeThreatxCondition <- split(StereotypeThreat, Condition)
StereotypeThreatMeans <- sapply(StereotypeThreatxCondition, mean)
StereotypeThreatxConditionPlot<- barplot2(StereotypeThreatMeans, xlab = "Condition", 
                                         ylim = c(1,5), ylab = "Mean", 
                                         names.arg = list("Small-Talk", "Fast-Friends"), 
                                         col = c("Grey", "SteelBlue"), xpd = FALSE, 
                                         main = "Stereotype Threat by Condition",
                                         sub = substitute(paste("H(1) = 0.005, ", 
                                                                       italic('p'), "= 0.94")))

#Communal Goal Affordance by Condition#
CommunalGoalAffordancexCondition <- split(CommunalValue, Condition)
CommunalGoalAffordanceMeans <- sapply(CommunalGoalAffordancexCondition, mean)
CommunalGoalAffordancexConditionPlot<- barplot2(CommunalGoalAffordanceMeans, xlab = "Condition",
                                                ylim = c(1,7), ylab = "Mean", 
                                                names.arg = list("Small-Talk", "Fast-Friends"),
                                                col = c("Grey", "SteelBlue"), xpd = FALSE,
                                                main = "Communal Goal Affordances by Condition",
                                                sub = substitute(paste("H(1) = 1.34, ", 
                                                                       italic('p'), "= 0.24")))
                                                
#State Anxiety by Condition#
StateAnxietyxCondition <- split(StateAnxiety, Condition)
StateAnxietyMeans <- sapply(StateAnxietyxCondition, mean)
StateAnxietyxConditionPlot<- barplot2(StateAnxietyMeans, xlab = "Condition",
                                                ylim = c(1,4), ylab = "Mean", 
                                                names.arg = list("Small-Talk", "Fast-Friends"),
                                                col = c("Grey", "SteelBlue"), xpd = FALSE,
                                                main = "State Anxiety by Condition",
                                                sub = substitute(paste("H(1) = 0.70, ", 
                                                                       italic('p'), "= 0.40")))

#Belonging by Condition#
BelongingxCondition <- split(Belonging, Condition)
BelongingMeans <- sapply(BelongingxCondition, mean)
BelongingxConditionPlot<- barplot2(BelongingMeans, xlab = "Condition",
                                                ylim = c(1,7), ylab = "Mean", 
                                                names.arg = list("Small-Talk", "Fast-Friends"),
                                                col = c("Grey", "SteelBlue"), xpd = FALSE,
                                                main = "Belonging by Condition",
                                                sub = substitute(paste("H(1) = 0.45, ", 
                                                                       italic('p'), "= 0.50")))

#Science Motivation by Condition#
ScienceMotivationxCondition <- split(ScienceMotivation, Condition)
ScienceMotivationMeans <- sapply(ScienceMotivationxCondition, mean)
ScienceMotivationxConditionPlot<- barplot2(ScienceMotivationMeans, xlab = "Condition",
                                                ylim = c(1,7), ylab = "Mean", 
                                                names.arg = list("Small-Talk", "Fast-Friends"),
                                                col = c("Grey", "SteelBlue"), xpd = FALSE,
                                                main = "Science Motivation by Condition",
                                                sub = substitute(paste("H(1) = 0.20, ", 
                                                                       italic('p'), "= 0.66")))

#Science Domain Identification by Condition#
ScienceDomainIdentificationxCondition <- split(ScienceDomainIdentification, Condition)
ScienceDomainIdentificationMeans <- sapply(ScienceDomainIdentificationxCondition, mean)
ScienceDomainIdentificationxConditionPlot <- barplot2(ScienceDomainIdentificationMeans, 
                                                      xlab = "Condition", ylim = c(1,5),
                                                      ylab = "Mean", names.arg = list
                                                      ("Small-Talk", "Fast-Friends"),
                                                      col = c("Grey", "Steelblue"), xpd = FALSE,
                                                      main = "Science Domain Identification 
                                                      by Condition", sub = substitute(paste(
                                                            "H(1) = 0.77, ", italic('p'),
                                                            "= 0.38")))

#Partner Ratings by Condition#
PartnerRatingsxCondition <- split(PartnerRatings, Condition)
PartnerRatingsMeans <- sapply(PartnerRatingsxCondition, mean)
PartnerRatingsxConditionPlot <- barplot2(PartnerRatingsMeans, xlab = "Condition", ylim = c(1,9),
                                                      ylab = "Mean", names.arg = list
                                                      ("Small-Talk", "Fast-Friends"),
                                                      col = c("Grey", "Steelblue"), xpd = FALSE,
                                                      main = "Partner Ratings by Condition", 
                                                      sub = substitute(paste("H(1) = 0.71, ",
                                                      italic('p'), "= 0.40")))
```
#Conduct Path Analysis for Study Model#
```{r}
#Create Correlation Matrix of Model Factors#
PathVariables <- c("Condition", "StereotypeThreat", "CommunalValue", 
                   "StateAnxiety", "Belonging", "ScienceMotivation")
Path.Matrix <- cov(TeamDynamicsData[PathVariables])

#Create Model for Path Analysis#
TeamDynamicsPath.Model = '
ScienceMotivation ~ D1*Belonging
Belonging ~ C2*StateAnxiety + C1*CommunalValue
CommunalValue ~ B1*StereotypeThreat
StateAnxiety ~ B2*StereotypeThreat
StereotypeThreat ~ A1*Condition
indirect1:= A1*B1*C1*D1
#Condition->StereotypeThreat->CommunalValue->Belonging->ScienceMotivation#
indirect2:= A1*B2*C2*D1
#Condition->StereotypeThreat->StateAnxiety->Belonging->ScienceMotivation#
'

#Run Path Analysis with 1000 Bootstrapped Items#
TeamDynamics.ModelFit <- lavaan::sem(data = TeamDynamicsData, TeamDynamicsPath.Model, sample.cov = Path.Matrix, sample.nobs = 152, se = "bootstrap", bootstrap = 1000)

#View Path Analysis Results#
summary(TeamDynamics.ModelFit, fit.measures = TRUE, standardized = TRUE)
```
#Visualize Path Model#
```{r}
TeamDynamics.Model <- semPaths(object = TeamDynamics.ModelFit, nCharNodes = 0, 
                               color = "steelblue", reorder = FALSE, intercepts = FALSE,
                               residuals = FALSE, thresholds = FALSE, whatLabels = "par", 
                               layout = "spring", springLevels = TRUE, rotation = 2)
```

